---
title: "Species Distribution Models Application (**sdmApp**)"
author: "Aboubacar HEMA"
date: "16/09/2020"
output:
   html_document:
     toc : TRUE
runtime: shiny 

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Installing R, **sdmApp** and other packages

This guide is based on the software package **sdmApp**, which is an add-on package for the statistical software R. Both R and **sdmApp**, as well as other R packages, are freely available from the CRAN (Comprehensive R Archive Network) website for Linux, Mac and Windows (<http://cran.r-project.org>). This website also offers descriptions of packages. Besides the standard version of R, there is a more user-friendly user interface for R: RStudio. RStudio is also freely available for Linux, Mac and Windows (<http://www.rstudio.com>). The **sdmApp** package is dependent on (i.e., uses) other R packages that must be installed on your computer before using **sdmApp**. Those will automatically be installed when installing **sdmApp**. For some functionalities, we use still other packages (such as foreign for reading data and some graphical packages). If so, this is indicated in the appropriate section in this guide. R, RStudio, the **sdmApp** package and its dependencies and other packages have regular updates. It is strongly recommended to regularly check for updates: this requires installing a new version for an update of R; with the update.packages() command or using the menu options in R or RStudio one can update the installed packages.

```{r cars, echo=FALSE, paged.print=TRUE}
numericInput("n",      "How many cars?", 5) 
renderTable({   head(cars, input$n) }) 
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
